---
title: "Differences in the mental health status, emotional regulation, and impulsivity traits in emerging adults from Argentina based on seasonal light variations"
author: "Dr. Lorena Cecilia López Steinmetz, PhD"
date: "09/09/2023"
output: html_document
---

## Note

This R code and the dataset corresponds to the paper entitled "Differences in the mental health status, emotional regulation, and impulsivity traits in emerging adults from Argentina based on seasonal light variations", authored by:

Lorena Cecilia López Steinmetz (1),(2)*, Candela Abigail Leyes (2), Maribel Eugenia Luque (1), Manuel Bruzzone (1), Juan Carlos Godoy (1)

(1) Instituto de Investigaciones Psicológicas (IIPsi), Facultad de Psicología, Universidad Nacional de Córdoba (UNC), Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET), Córdoba, Argentina.

(2) Decanato de Ciencias Sociales, Universidad Siglo 21, Córdoba, Argentina.

* Corresponding author: Dr. Lorena Cecilia López Steinmetz, PhD. Laboratorio de Psicología, Instituto de Investigaciones Psicológicas (IIPsi), Facultad de Psicología, Universidad Nacional de Córdoba (UNC), Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET). Boulevard de La Reforma and Enfermera Gordillo, s/n, 2nd floor. Córdoba, Argentina. Zip Code: 5000. Email: cecilialopezsteinmetz@unc.edu.ar 



## Data: Time 1

Load the dataset


```{r echo=TRUE, warning=FALSE}
# install.packages("openxlsx")

library(readxl)

results_survey339868_3_T1 <- read_excel("C:/Users/stein/OneDrive/Escritorio/results-survey_dataset.xlsx", sheet = 1)

# Check the structure of the data
str(results_survey339868_3_T1)
```

#### Dataset

Verifying the correct upload of the dataset.

```{r, echo=TRUE}
dataset_t1 <- results_survey339868_3_T1

# summary(dataset_t1)

names(dataset_t1)
```


Select variables to be used in the analysis

```{r , echo=TRUE}
selected_vars_t1 <- dataset_t1[, c("6. ¿En qué provincia vivís actualmente?",
                             "7. ¿Cuál es tu sexo biológico?:",
                             "8. ¿Cuál es tu identidad de género?:",
                             "8. ¿Cuál es tu identidad de género?:   [Otro]",
                             "10. ¿Alguna vez un profesional de la salud (psicólogo/a, psiquiatra u otro/o médico/a) te diagnosticó algún problema de salud mental? (por ejemplo, depresión, trastorno de ansiedad o cualquier otro)",
                             "11. ¿Alguna vez intentaste suicidarte?",
                             "12. Sólo en caso de que hayas respondido sí a la pregunta anterior, ¿cuántas veces intentaste suicidarte? (completá sólo con números)",
                             "¿Cuál de estas bebidas alcohólicas es la que consumís más frecuentemente?  Si tomás otra bebida que no está en la lista, indicá la opción de la lista que sea la más parecida a la bebida que vos tomás.",
                             "Teniendo en cuenta la bebida alcohólica que indicaste que consumís más frecuentemente:   ¿cuántos vasos, copas, latas o medidas (según corresponda en la imagen) de esa bebida acostumbrás a tomar generalmente en una misma ocasión?  Tené en cuenta que en “una misma ocasión” significa en una misma salida, una misma tarde o noche o en una misma juntada.  Respondé con la cantidad que tomás generalmente, la mayoría de las veces.  Si nunca tomás alcohol respondé 0.",
                             "Cualquiera sea la bebida alcohólica que tomás, durante el último mes, ¿tomaste alcohol hasta emborracharte?",
                             "¿A qué edad aproximadamente probaste por primera vez alguna bebida alcohólica?  Si nunca tomaste alcohol respondé 0.",
                             "BYAACQ",
                             "DEPRBECK",
                             "STAIRASGO",
                             "POSURG", 
                             "NEGURG",
                             "PERSEVLACK",
                             "PREMEDLACK",
                             "SENSSEEK",
                             "ISOSUIC",
                             "DERSAFECTONEG",
                             "DERSAFECTOPOSIT")]
```



Create a new dataset with selected variables and show a summary of it


```{r , echo=TRUE}
data_t1 <- data.frame(selected_vars_t1)

summary(data_t1)
```


**Create the variable "Regions"**

Create the variable "regions" by grouping provinces located on the north, center, and south of the country.


```{r , echo=TRUE}
data_t1$region<-data_t1$X6...En.qué.provincia.vivís.actualmente.

table(data_t1$region)

# Create a new variable "factor_region" with grouped categories
data_t1$factor_region <- ifelse(data_t1$region %in% c("JUJ", "SAL", "TUC", "CAT", "STGOE", "FORM", "CHAC", "CORRI", "MISIO"), 
                             "north",
                             ifelse(data_t1$region %in% c("LRIOJ", "SJUAN", "MENDO", "CBA", "STAFE", "ENTRI", "LPAMP", "BA", "CABA"),
                                    "center",
                                    "south")) # "NEUQU", "RIONE", "CHUBU" , "STACR", "TDELF"


# print(data_t1$factor_region) # Print the updated dataset

summary(data_t1$factor_region)
```


Get the names of the variables in this dataset named "data_t1" and print out the variable names


```{r , echo=TRUE}
variable_names_t1 <- names(data_t1)

print(variable_names_t1)
```


**Biological sex**

(0 = male, 1 = female)

```{r , echo=TRUE}
# Get the table of counts
sex_counts_t1 <- table(data_t1$X7...Cuál.es.tu.sexo.biológico..)

# Print the results with labels
cat("Male =", sex_counts_t1[1], "\n")
cat("Female =", sex_counts_t1[2], "\n")


# Get the table of percentages
sex_perc_t1 <- prop.table(table(data_t1$X7...Cuál.es.tu.sexo.biológico..)) * 100

# Print the results with labels
cat("Male =", sex_perc_t1[1], "% \n")
cat("Female =", sex_perc_t1[2], "% \n")
```



**Regions**

```{r , echo=TRUE}
table(data_t1$factor_region)

prop.table(table(data_t1$factor_region)) * 100
```


**Suicidal behavior history**

(0 = without suicidal behavior background, 1 = suicidal ideation history, 2 = suicide attempt history)


```{r , echo=TRUE}
table(data_t1$X11...Alguna.vez.intentaste.suicidarte.)

prop.table(table(data_t1$X11...Alguna.vez.intentaste.suicidarte.)) * 100
```


**Mental disorder history** 

(0 = no, 1 = yes)


```{r , echo=TRUE}
table(data_t1$X10...Alguna.vez.un.profesional.de.la.salud..psicólogo.a..psiquiatra.u.otro.o.médico.a..te.diagnosticó.algún.problema.de.salud.mental...por.ejemplo..depresión..trastorno.de.ansiedad.o.cualquier.otro.)

prop.table(table(data_t1$X10...Alguna.vez.un.profesional.de.la.salud..psicólogo.a..psiquiatra.u.otro.o.médico.a..te.diagnosticó.algún.problema.de.salud.mental...por.ejemplo..depresión..trastorno.de.ansiedad.o.cualquier.otro.)) * 100
```


**Age of onset on alcohol consumption**

(Never consumed alcohol = 0)

```{r , echo=TRUE}
table(data_t1$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

prop.table(table(data_t1$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)) * 100
```



```{r , echo=TRUE}
summary(data_t1$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

mean(data_t1$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

sd(data_t1$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

range(data_t1$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

# Sort the values in ascending order
sorted_age_of_onset_t1 <- sort(data_t1$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

# Display the sorted values
sorted_age_of_onset_t1
```


**Drinking alcohol until get drunk during the last month**

(0 = Never consumed alcohol, 1 = Yes, 2 = N0)

```{r , echo=TRUE}
table(data_t1$Cualquiera.sea.la.bebida.alcohólica.que.tomás..durante.el.último.mes...tomaste.alcohol.hasta.emborracharte.)

prop.table(table(data_t1$Cualquiera.sea.la.bebida.alcohólica.que.tomás..durante.el.último.mes...tomaste.alcohol.hasta.emborracharte.)) * 100
```


**Negative consequences of alcohol consumption (BYAACQ)**

```{r , echo=TRUE}
mean(data_t1$BYAACQ)

sd(data_t1$BYAACQ)

range(data_t1$BYAACQ)
```


**Depression (BDI-II)**


```{r , echo=TRUE}
mean(data_t1$DEPRBECK)

sd(data_t1$DEPRBECK)

range(data_t1$DEPRBECK)
```


**Anxiety trait (STAI-T)**


```{r , echo=TRUE}
mean(data_t1$STAIRASGO)

sd(data_t1$STAIRASGO)

range(data_t1$STAIRASGO)
```


**Suicidal risk (ISO-30)**


```{r , echo=TRUE}
mean(data_t1$ISOSUIC)

sd(data_t1$ISOSUIC)

range(data_t1$ISOSUIC)
```


**Regulation of negative emotions (DERS-N)**


```{r , echo=TRUE}
mean(data_t1$DERSAFECTONEG)

sd(data_t1$DERSAFECTONEG)

range(data_t1$DERSAFECTONEG)
```



**Regulation of positive emotions (DERS-P)**


```{r , echo=TRUE}
mean(data_t1$DERSAFECTOPOSIT)

sd(data_t1$DERSAFECTOPOSIT)

range(data_t1$DERSAFECTOPOSIT)
```


**Impulsivity-related traits (UPPS-P)**


**Negative urgency**


```{r , echo=TRUE}
mean(data_t1$NEGURG)

sd(data_t1$NEGURG)

range(data_t1$NEGURG)
```


**Positive urgency**


```{r , echo=TRUE}
mean(data_t1$POSURG)

sd(data_t1$POSURG)

range(data_t1$POSURG)
```


**Lack of perseverance**


```{r , echo=TRUE}
mean(data_t1$PERSEVLACK)

sd(data_t1$PERSEVLACK)

range(data_t1$PERSEVLACK)
```


**Lack of premeditation**


```{r , echo=TRUE}
mean(data_t1$PREMEDLACK)

sd(data_t1$PREMEDLACK)

range(data_t1$PREMEDLACK)
```


**Sensation seeking**


```{r , echo=TRUE}
mean(data_t1$SENSSEEK)

sd(data_t1$SENSSEEK)

range(data_t1$SENSSEEK)
```




## Data: Time 2

Load the dataset

```{r, echo=TRUE, warning=FALSE}
# install.packages("openxlsx")

library(readxl)

results_survey339868_3_ <- read_excel("C:/Users/stein/OneDrive/Escritorio/results-survey_dataset.xlsx", sheet = 2)

# Check the structure of the data
str(results_survey339868_3_)
```

#### Dataset

Verifying the correct upload of the dataset.

```{r , echo=TRUE}
dataset <- results_survey339868_3_

# summary(dataset)

names(dataset)
```


Select variables to be used in the analysis

```{r , echo=TRUE}
selected_vars <- dataset[, c("6. ¿En qué provincia vivís actualmente?",
                             "7. ¿Cuál es tu sexo biológico?:",
                             "8. ¿Cuál es tu identidad de género?:",
                             "8. ¿Cuál es tu identidad de género?:   [Otro]",
                             "10. ¿Alguna vez un profesional de la salud (psicólogo/a, psiquiatra u otro/o médico/a) te diagnosticó algún problema de salud mental? (por ejemplo, depresión, trastorno de ansiedad o cualquier otro)",
                             "11. ¿Alguna vez intentaste suicidarte?",
                             "12. Sólo en caso de que hayas respondido sí a la pregunta anterior, ¿cuántas veces intentaste suicidarte? (completá sólo con números)",
                             "¿Cuál de estas bebidas alcohólicas es la que consumís más frecuentemente?  Si tomás otra bebida que no está en la lista, indicá la opción de la lista que sea la más parecida a la bebida que vos tomás.",
                             "Teniendo en cuenta la bebida alcohólica que indicaste que consumís más frecuentemente:   ¿cuántos vasos, copas, latas o medidas (según corresponda en la imagen) de esa bebida acostumbrás a tomar generalmente en una misma ocasión?  Tené en cuenta que en “una misma ocasión” significa en una misma salida, una misma tarde o noche o en una misma juntada.  Respondé con la cantidad que tomás generalmente, la mayoría de las veces.  Si nunca tomás alcohol respondé 0.",
                             "Cualquiera sea la bebida alcohólica que tomás, durante el último mes, ¿tomaste alcohol hasta emborracharte?",
                             "¿A qué edad aproximadamente probaste por primera vez alguna bebida alcohólica?  Si nunca tomaste alcohol respondé 0.",
                             "BYAACQ",
                             "DEPRBECK",
                             "STAIRASGO",
                             "POSURG", 
                             "NEGURG",
                             "PERSEVLACK",
                             "PREMEDLACK",
                             "SENSSEEK",
                             "ISOSUIC",
                             "DERSAFECTONEG",
                             "DERSAFECTOPOSIT")] 
```



Create a new dataset with selected variables and show a summary of it


```{r , echo=TRUE}
data <- data.frame(selected_vars)

summary(data)
```


**Create the variable "Regions"**

Create the variable "regions" by grouping provinces located on the north, center, and south of the country.


```{r , echo=TRUE}
data$region<-data$X6...En.qué.provincia.vivís.actualmente.

table(data$region)

# Create a new variable "factor_region" with grouped categories
data$factor_region <- ifelse(data$region %in% c("JUJ", "SAL", "TUC", "CAT", "STGOE", "FORM", "CHAC", "CORRI", "MISIO"), 
                             "north",
                             ifelse(data$region %in% c("LRIOJ", "SJUAN", "MENDO", "CBA", "STAFE", "ENTRI", "LPAMP", "BA", "CABA"),
                                    "center",
                                    "south")) # "NEUQU", "RIONE", "CHUBU" , "STACR", "TDELF"

# Print the updated dataset
# print(data$factor_region)

summary(data$factor_region)
```


Get the names of the variables in this dataset named "data" and print out the variable names


```{r , echo=TRUE}
variable_names <- names(data)

print(variable_names)
```



**Percentage of attrition from T1 (N = 1184) to T2 (N = 490)**

```{r , echo=TRUE}
# Number of participants at T1 and T2
participants_t1 <- 1184
participants_t2 <- 490

# Calculate the percentage of desertion
desertion_percentage <- ((participants_t1 - participants_t2) / participants_t1) * 100

# Print the result
cat("Percentage of participants' attrition from T1 to T2:", desertion_percentage, "%\n")
```


**Biological sex**

(0 = male, 1 = female)

```{r , echo=TRUE}
# Get the table of counts
sex_counts <- table(data$X7...Cuál.es.tu.sexo.biológico..)

# Print the results with labels
cat("Male =", sex_counts[1], "\n")
cat("Female =", sex_counts[2], "\n")


# Get the table of percentages
sex_perc <- prop.table(table(data$X7...Cuál.es.tu.sexo.biológico..)) * 100

# Print the results with labels
cat("Male =", sex_perc[1], "% \n")
cat("Female =", sex_perc[2], "% \n")
```



**Regions**

```{r , echo=TRUE}
table(data$factor_region)

prop.table(table(data$factor_region)) * 100
```


**Suicidal behavior history**

(0 = without suicidal behavior background, 1 = suicidal ideation history, 2 = suicide attempt history)


```{r , echo=TRUE}
table(data$X11...Alguna.vez.intentaste.suicidarte.)

prop.table(table(data$X11...Alguna.vez.intentaste.suicidarte.)) * 100
```


**Mental disorder history** 

(0 = no, 1 = yes)


```{r , echo=TRUE}
table(data$X10...Alguna.vez.un.profesional.de.la.salud..psicólogo.a..psiquiatra.u.otro.o.médico.a..te.diagnosticó.algún.problema.de.salud.mental...por.ejemplo..depresión..trastorno.de.ansiedad.o.cualquier.otro.)

prop.table(table(data$X10...Alguna.vez.un.profesional.de.la.salud..psicólogo.a..psiquiatra.u.otro.o.médico.a..te.diagnosticó.algún.problema.de.salud.mental...por.ejemplo..depresión..trastorno.de.ansiedad.o.cualquier.otro.)) * 100
```


**Age of onset on alcohol consumption**

(Never consumed alcohol = 0)

```{r , echo=TRUE}
summary(data$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

mean(data$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

sd(data$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

range(data$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

# Sort the values in ascending order
sorted_age_of_onset_t2 <- sort(data$X.A.qué.edad.aproximadamente.probaste.por.primera.vez.alguna.bebida.alcohólica...Si.nunca.tomaste.alcohol.respondé.0.)

# Display the sorted values
sorted_age_of_onset_t2
```


**Drinking alcohol until get drunk during the last month**

(0 = Never consumed alcohol, 1 = Yes, 2 = N0)

```{r , echo=TRUE}
table(data$Cualquiera.sea.la.bebida.alcohólica.que.tomás..durante.el.último.mes...tomaste.alcohol.hasta.emborracharte.)

prop.table(table(data$Cualquiera.sea.la.bebida.alcohólica.que.tomás..durante.el.último.mes...tomaste.alcohol.hasta.emborracharte.)) * 100
```


**Negative consequences of alcohol consumption (BYAACQ)**


```{r , echo=TRUE}
mean(data$BYAACQ)

sd(data$BYAACQ)

range(data$BYAACQ)
```


**Depression (BDI-II)**


```{r , echo=TRUE}
mean(data$DEPRBECK)

sd(data$DEPRBECK)

range(data$DEPRBECK)
```


**Anxiety trait (STAI-T)**


```{r , echo=TRUE}
mean(data$STAIRASGO)

sd(data$STAIRASGO)

range(data$STAIRASGO)
```


**Suicidal risk (ISO-30)**


```{r , echo=TRUE}
mean(data$ISOSUIC)

sd(data$ISOSUIC)

range(data$ISOSUIC)
```


**Regulation of negative emotions (DERS-N)**


```{r , echo=TRUE}
mean(data$DERSAFECTONEG)

sd(data$DERSAFECTONEG)

range(data$DERSAFECTONEG)
```


**Regulation of positive emotions (DERS-P)**


```{r , echo=TRUE}
mean(data$DERSAFECTOPOSIT)

sd(data$DERSAFECTOPOSIT)

range(data$DERSAFECTOPOSIT)
```


**Impulsivity-related traits (UPPS-P)**


**Negative urgency**


```{r , echo=TRUE}
mean(data$NEGURG)

sd(data$NEGURG)

range(data$NEGURG)
```


**Positive urgency**


```{r , echo=TRUE}
mean(data$POSURG)

sd(data$POSURG)

range(data$POSURG)
```


**Lack of perseverance**


```{r , echo=TRUE}
mean(data$PERSEVLACK)

sd(data$PERSEVLACK)

range(data$PERSEVLACK)
```


**Lack of premeditation**


```{r , echo=TRUE}
mean(data$PREMEDLACK)

sd(data$PREMEDLACK)

range(data$PREMEDLACK)
```


**Sensation seeking**


```{r , echo=TRUE}
mean(data$SENSSEEK)

sd(data$SENSSEEK)

range(data$SENSSEEK)
```




## Data: Time 1 and Time 2

Load the dataset

```{r, echo=TRUE, warning=FALSE}
# install.packages("openxlsx")

library(readxl)

data_t1_t2 <- read_excel("C:/Users/stein/OneDrive/Escritorio/results-survey_dataset.xlsx", sheet = 3)

# Check the structure of the data
str(data_t1_t2)
```


```{r , echo=TRUE}
names(data_t1_t2)
```


Select variables to be used in the analysis


```{r , echo=TRUE}
data_t1_t2 <- data_t1_t2[, c("groups",
                             "BYAACQ",
                             "DEPRBECK",
                             "STAIRASGO",
                             "POSURG", 
                             "NEGURG",
                             "PERSEVLACK",
                             "PREMEDLACK",
                             "SENSSEEK",
                             "ISOSUIC",
                             "DERSAFECTONEG",
                             "DERSAFECTOPOSIT")] 
```


```{r , echo=TRUE}
summary(data_t1_t2)
```




**Testing differences between groups (not paired samples) for each variable**


```{r , echo=TRUE, warning=FALSE}
# List of variable names for which to calculate differences and perform tests
variable_names_t1_t2 <- c("BYAACQ", "DEPRBECK", "STAIRASGO", "ISOSUIC", "DERSAFECTONEG", "DERSAFECTOPOSIT", "NEGURG", "POSURG", "PERSEVLACK", "PREMEDLACK", "SENSSEEK") 
```


```{r message=FALSE, warning=FALSE, , echo=TRUE}
library(dplyr)
library(purrr)

# Function to perform Wilcoxon rank-sum test
perform_wilcox_rank_sum_test <- function(variable) {
  group1_data <- data_t1_t2 %>%
    filter(groups == "a") %>%
    pull(!!sym(variable))
  
  group2_data <- data_t1_t2 %>%
    filter(groups == "b") %>%
    pull(!!sym(variable))
  
  # Check for non-missing observations
  if (sum(!is.na(group1_data)) > 0 && sum(!is.na(group2_data)) > 0) {
    wilcox_test_result <- wilcox.test(group1_data, group2_data, alternative = "two.sided")
    
    # Output test statistic in the results
    result <- list(
      Variable = variable,
      Statistic = wilcox_test_result$statistic,
      P_Value = wilcox_test_result$p.value
    )
    
    return(result)
  } else {
    cat("Variable:", variable, "has missing or insufficient data. Skipping...\n")
    return(NULL)
  }
}

# Perform Wilcoxon rank-sum test for each variable
test_results <- map(variable_names_t1_t2, perform_wilcox_rank_sum_test)

# Print the test results
for (i in seq_along(test_results)) {
  if (!is.null(test_results[[i]])) {
    cat("Variable:", test_results[[i]]$Variable, "\n")
    cat("Statistic:", test_results[[i]]$Statistic, "\n")
    cat("P-value:", test_results[[i]]$P_Value, "\n\n")
  }
}
```


This plot is exclusively for visualizing significant results:


```{r message=FALSE, warning=FALSE, , echo=TRUE}
library(ggplot2)
library(gridExtra)

# Create a list to store plots
plot_list <- list()

# Create plots for significant variables
for (var_name in variable_names_t1_t2) {
  group1_data <- data_t1_t2 %>%
    filter(groups == "a") %>%
    pull(!!sym(var_name))
  
  group2_data <- data_t1_t2 %>%
    filter(groups == "b") %>%
    pull(!!sym(var_name))
  
  # Check for non-missing observations
  if (sum(!is.na(group1_data)) > 0 && sum(!is.na(group2_data)) > 0) {
    p_value <- wilcox.test(group1_data, group2_data, alternative = "two.sided")$p.value
    
    # Create a box plot if p-value is significant (e.g., < 0.05)
    if (p_value < 0.05) {
      # Truncate the longer group to match the length of the shorter group
      min_length <- min(length(group1_data), length(group2_data))
      group1_data <- group1_data[1:min_length]
      group2_data <- group2_data[1:min_length]
      
      plot_title <- paste("Comparison of", var_name, "(p-value:", p_value, ")")
      data_for_plot <- data.frame(Value = c(group1_data, group2_data),
                                  Group = factor(rep(c("Group a", "Group b"), each = min_length)))
      
      current_plot <- ggplot(data_for_plot, aes(x = Group, y = Value, fill = Group)) +
  geom_boxplot() +
  ggtitle(plot_title) +
  theme(plot.title = element_text(size = 8))  # Adjust the size as needed

      
      plot_list[[var_name]] <- current_plot
    }
  }
}

# Arrange and display the plots
grid.arrange(grobs = plot_list, ncol = 2)  # Adjust ncol as needed
```















